R Notebook

### 2021-08-11 gc_ramp_comparison.Rmd
new resolution plot

---
title: "R Notebook"
output: html_notebook
---

```{r, include=FALSE}
# Libraries
library(tidyverse) # What are we without the tidyverse? c:
library(plotly)
library(ggrepel)
library(ggsci)
library(ggsignif)
library(ggdist)

@@

@@

# Overview Plot
```{r, fig.width=8, fig.height=4, warning=FALSE}
# Overview Plot
p_bame_overview <- results %>%
  ggplot() +
    aes(x = `Retention Time`, y = `Relative Height`, fill = ramp) +
    geom_col(width = 0.1) +
    facet_wrap(.~ramp, ncol = 1) +
    ggtitle("FAME Standards Overview") +
    theme_bw() +
    scale_fill_npg() +
    theme(legend.position = "bottom")
p_bame_overview
```

```{r}
p_bame_resolution <- peak_analysis %>% 
  filter(!is.na(`Resolution (EP)`)) %>% 
  ggplot() +
  aes(x = `Resolution (EP)`, y = ramp) +
  stat_slab(aes(color = ramp,
                fill = ramp), 
            height = 0.5) +
   geom_point(aes(color = ramp, y = as.numeric(ramp) - 0.15),
             size = 2, 
             alpha = 0.3) +
  stat_pointinterval() +
  ggtitle("DB5-HT 30m Resolution Versus Ramp Rate") +
  xlab("Resolution (EP)") +
  ylab("Ramp Rate (C per min)") +
  scale_color_npg() +
  scale_fill_npg() +
  theme_minimal()
p_bame_resolution
```

## Save Images
```{r}
ggsave("fig_output/p_bame_overview.png", p_bame_overview)
```

>>>>

---
title: "R Notebook"
output: html_document
---

```{r, include=FALSE}
# Libraries
library(tidyverse) # What are we without the tidyverse? c:
library(plotly)
library(ggrepel)
library(ggsci)
library(ggsignif)
library(ggdist)
library(ggborderline)

@@

# Overview Plot
Here we see the retention times of BAME standard compounds across 5 GC ramps ranging from 1 to 5 C per minute.
```{r, fig.width=8, fig.height=4, warning=FALSE}
# Overview Plot
p_bame_overview <- results %>%
  ggplot() +
    aes(x = `Retention Time`, y = `Relative Height`, fill = ramp) +
    geom_col(width = 0.1) +
    facet_wrap(.~ramp, ncol = 1) +
    ggtitle("FAME Standards Overview") +
    theme_bw() +
    scale_fill_npg() +
    theme(legend.position = "bottom")
p_bame_overview
```

```{r}
p_bame_resolution <- peak_analysis %>% 
  filter(!is.na(`Resolution (EP)`)) %>% 
  ggplot() +
  aes(x = `Resolution (EP)`, y = ramp) +
  stat_slab(aes(color = ramp,
                fill = ramp), 
            height = 0.5) +
   geom_point(aes(color = ramp, y = as.numeric(ramp) - 0.15),
             size = 2, 
             alpha = 0.3) +
  stat_pointinterval() +
  ggtitle("DB5-HT 30m Resolution Versus Ramp Rate") +
  xlab("Resolution (EP)") +
  ylab("Ramp Rate (C per min)") +
  scale_color_npg() +
  scale_fill_npg() +
  theme_minimal()
p_bame_resolution
```
```{r}
p_bame_resolution2 <- peak_analysis %>% 
  filter(!is.na(`Resolution (EP)`)) %>% 
  ggplot() +
  aes(y = `Resolution (EP)`, x = `ramp`, color = `Peak Name`, group = `Peak Name`) + 
  geom_point() +
  geom_path() +
  scale_color_viridis_d() +
  ggtitle("DB5-HT 30m Resolution Versus Ramp Rate") +
  ylab("Resolution (EP)") +
  xlab("Ramp Rate (C per min)") +
  theme_minimal()
p_bame_resolution2
```

## Save Images
```{r}
ggsave("fig_output/p_bame_overview.png", p_bame_overview, height = 7, width = 11, dpi = 300)
ggsave("fig_output/p_bame_resolution.png", p_bame_resolution)
ggsave("fig_output/p_bame_resolution2.png", p_bame_resolution2)
```

@@
